# Logistic Regression With A Non-Linear Decision Boundary

## Modelling

You may specify the model and regularize (or not) in any way you wish, just be sure to clearly state your final model.

Vanilla Model

```{r}
# Vanilla Logistic Regression Model
log_mod <- glm(Revenue ~ ., family = binomial,data = train)
log_mod %>% 
  tidy() %>%
  kable(digits = 2, caption = 'Vanilla Logistic Regression Model')
```

Polynomial Logistic Regression Models (choose the variables to make 5th degree polynomials by looking at the most significant numerical variables from the vanilla model)

1.  Polynomial Logistic Model with all variables

```{r}
poly_log1 <- glm(Revenue ~ 
            Informational + I(Informational^2) + I(Informational^3) +I(Informational^4) + 
            ProductRelated_Duration + I(ProductRelated_Duration^2) + I(ProductRelated_Duration^3) + I(ProductRelated_Duration^4) +
            ExitRates + I(ExitRates^2) + I(ExitRates^3) + I(ExitRates^4) + 
            PageValues + I(PageValues^2) + I(PageValues^3) + I(PageValues^4) + .
            ,data = train, family = 'binomial')
poly_log1 %>% 
  tidy() %>%
  kable(digits = 2, caption = 'Polynomial logistic regression model fitted to the online shopping dataset using all the varibles')
```

2.  Polynomial Logistic Model with only the polynomial variables

```{r}
poly_log2 <- glm(Revenue ~ 
            Informational + I(Informational^2) + I(Informational^3) +I(Informational^4) + 
            ProductRelated_Duration + I(ProductRelated_Duration^2) + I(ProductRelated_Duration^3) + I(ProductRelated_Duration^4) +
            ExitRates + I(ExitRates^2) + I(ExitRates^3) + I(ExitRates^4) + 
            PageValues + I(PageValues^2) + I(PageValues^3) + I(PageValues^4) 
            ,data = train, family = 'binomial')
poly_log2 %>% 
  tidy() %>%
  kable(digits = 2, caption = 'Polynomial logistic regression model fitted to the online shopping dataset using only the polynomial variables')

```

------------------------------------------------------------------------

\newpage

## Inference/Interpretation

------------------------------------------------------------------------

\newpage

## Optimizing F1 Score

------------------------------------------------------------------------

\newpage

## Prediction
